---
title: "HTN HTE Analysis"
author: "Jingzhi Kevin Yu"
date: "4/15/24"
output: html_document
---

# STEP 0A: Extract Data from Database

## Setup 
1. Load relevant database connection tools 
2. Get working directory which will be used to create folders to save results
```{r, setup}
if (!require(DatabaseConnector))
{
  install.packages("DatabaseConnector")
}
if (!require(SqlRender))
{
  install.packages("SqlRender")
}

library(DatabaseConnector)
library(SqlRender)
library(tidyverse)

# get working directory or set your own
path = getwd()

# medication type list
htn_med_list = c('acei', 'arb', 'ccb', 'diuretics', 'acei_arb_diuretic')
```

#### INPUT CHUNK ####

## SQL CONNECTION
INSTRUCTIONS:
1. Select SQL type 
2. Edit SQL log-on info
```{r}
## Select SQL type
sql_flavor = 'sqlite' #'sqlite' # change here ('sqlite', 'ms-sql', 'postgres')


if (sql_flavor == 'ms-sql')
{
  Sys.setenv("DATABASECONNECTOR_JAR_FOLDER" = "c:/Development")
  downloadJdbcDrivers("sql server")
  
  connectionDetails = createConnectionDetails(
    dbms = "sql server",
    server = Sys.getenv("HTE_HTN_DB_SERVER"),
    user = Sys.getenv("HTE_HTN_DB_USER"),
    password = Sys.getenv("HTE_HTN_DB_PASSWORD"),
    pathToDriver="C:/Development"
  )
  conn = connect(connectionDetails)
} else if (sql_flavor == 'postgres')
{
  Sys.setenv("DATABASECONNECTOR_JAR_FOLDER" = "c:/Development")
  downloadJdbcDrivers("postgresql")
  
  connectionDetails = createConnectionDetails(
    dbms = "postgresql",
    server = Sys.getenv("HTE_HTN_DB_SERVER"),
    user = Sys.getenv("HTE_HTN_DB_USER"),
    password = Sys.getenv("HTE_HTN_DB_PASSWORD"),
    pathToDriver="C:/Development"
  )
  conn = connect(connectionDetails)
} else if (sql_flavor == 'sqlite')
{ 
    if (!require(RSQLite))
  {
    install.packages("RSQLite")
  }
    library(RSQLite)
    conn = connect(dbms = "sqlite", server = '/Users/excenity/Documents/HSIP/Research/Dissertation Project/Data/EDW OMOP.db')
    cdmDbSchema = 'main'
}
```

## INTERMEDIATE FILES
--> Determine whether analytic dataset will be saved for future analysis. 
--> If not saved, analytic dataset (`final_df.csv`) must be generated via the `Data Querying` codes prior to running the analysis scripts 
  (Steps 1, 2, 3) 
--> If saved, once the analytic dataset (`final_df.csv`) has been produced, analysis can be run directly from Step 1.
```{r}
# Export analytic dataset for future analysis?
output_analytical_dataset = F
```


#### SCRIPTS ####

--- Data Querying ---

## Query Code
```{r}
if (sql_flavor == 'ms-sql')
{
  source(file.path(path, 'STEP0A_DatasetCreation_MSSQL.R'))
} else if (sql_flavor == 'sqlite')
{
  source(file.path(path, 'STEP0A_DatasetCreation_SQlite.R'))
} else if (sql_flavor == 'postgres')
{
  source(file.path(path, 'STEP0A_DatasetCreation_Postgres.R'))
}
```

# STEP 0B: Analytic Dataset Creation

## Run Data Wrangling Code
```{r}
source('STEP0B_dataset_creation_script.R')

if (output_analytical_dataset == T)
{
  write.csv(final_df, 'final_df.csv', row.names = F)
  remove(final_df)
}
```

--- Statistical Analysis ---

## PART 1: Explore patient characteristics that contribute to HTE

# STEP 1: Individual Treatment Effects (ITE) Estimation via G-estimation
```{r}
source('STEP1_ITE_estimation.R')
```

# STEP 2: Causal Forest to Identify Factors Contributing Most to Heterogeneity
```{r}
source('STEP2_CF_HTE.R')
```

## -- STOP HERE AND REVIEW RESULTS OF STEP 2 -- ## 


## PART 2: Use targeted estimation to determine treatment effects of BP medications

# STEP 3: Targeted Maximum Likelihood Estimation (TMLE) of Medication Treatment Effects within Different Patient Populations
```{r}
# input variables of importance used for creating patient profiles
cont_var = c('age', 'SBP', 'DBP', 'BMI', 'total_cholesterol', 'creatinine')

# input cutoffs of variables used for creating patient profiles 
cutpoints = list(c(0, 65, 150), 
                 c(0 ,150, 300), 
                 c(0, 90, 200), 
                 c(0, 30, 100), 
                 c(0, 200, 300), 
                 c(0, 0.95, 5))

source('STEP3_TMLE_HTE.R')
```
